---
# Creating and assigning our global variables
title: "Behaviour Duration Report"
# Output file type
output: html_document
# Set the date based on your computer
date: "`r Sys.Date()`"
# Set default parameters
params:
  base_path: "C:/Users/user/Desktop/Oakleigh_Project/AccelerometerData/Accelerometer_Analysis"
  dataset_name: ""
  sample_rate: ""
---

```{r Setup, include=FALSE}
# Set the variables of our other chunks
knitr::opts_chunk$set(
  # Set so that for all of our plots, it won't include the code.
  echo = FALSE,
  # Set the global figure width.
  fig.width = 5.625,
  # Set the global figure height.
  fig.height = 4.5,
  # Stops messages from being produced in the output
  message = FALSE,
  # Stops warnings from appearing in the output
  warning = FALSE)

  # We need to check if the user has all the right packages installed and if they don't install them.
# At this point we're just loading the packages but we need to change that.
```

```{r Load in Data, include = TRUE}

# Attempt to load in the training data
training_data <- loadTrainingData()

```

# Behaviour Classification of Individuals

### The data used for this split is: `r dataset_name`
<br>
Below is a graph of all individuals classed by behaviours in minutes.
The point of this plot is to use it to determine what your ideal window length is, which will be used to generate statistical and time series features.

## Using this report to generate features:
Window lengths are used to condense multiple observations into a single row of data. 
<br>

## Visualising your data before processing:
One of the more important and overlooked steps of processing data is visualising it for the purposes of determining if your behaviours are internally consistent compared to themselves and other behaviours.

```{r Create Trace Figure Data, fig.height=8, fig.width = 14, dpi = 100, out.width="100%", out.height="100%", echo = FALSE}
  # Plot an example of trace signalling.
  printer <- plotTraceExamples(behaviours = unique(training_data$Activity),data = training_data, n_samples = 200, individuals = 6)
  print(printer)
```

### Features:
Generating features is a process of taking variables within multiple rows of a dataframe and generating additional variables in a long column for use in statistical analysis. To generate time and statistical features within accelerometer data we require:
<ul>
<li>The sample rate of the accelerometer (in seconds) used in the study</li>
<li>The overlap percentage of our windows.</li>
<li>The window length (in seconds).</li>
</ul>
<br>

### Windows:
Within timeseries data, windows are segments of the dataset that are used to generate rolling statistics. 
<br><br>

#### Overlap Percentage:
The overlap percentage determines how much of the windows overlap. This can be beneficial for minimising the risk that behaviours are missed by a window length being placed between two behaviours. Increasing window overlap percentage will increase how many total windows are produced, this can increase how many data points you can analyse but also increases the computing time and power necessary to generate features, particularly within large datasets. Some studies (cite) indicate that little value is to be gained from increasing your overlap percentage above 50%.
<br>
If you are unsure, set your overlap percentage to 50%.
<br><br>

#### Window Length:
Larger window lengths can increase your chance of capturing multiple behaviours within a single feature. Shorter lengths decrease your chances of capturing entire behaviours. As a general rule, you should set your window length to be the same as the smallest of your all behaviours lower-quantiles. You may however want to select based on the the smallest median behaviour duration instead. This will ensure your likelihood of capturing the entirety of a single behaviour and it not being confused with another.
<br>
For example, if you have three behaviours named: Jumping, Turning and Sitting, with lower quantile duration in seconds of: 2, 4 and 30 respectfully, you would be best to select a window length of two seconds, based on the duration of Jumping. However you may want to base your window length off of your shortest median behaviour length instead for example. The plot and tables below include information on all of these numbers to help you make this decision.
<br><br>

<h2 style="text-align: center;">Behaviour Duration by Activity</h2>
<!-- Generate all of the behaviour duration data and plot the behaviour duration plot -->
```{r Create Plot Data, fig.height=8, fig.width = 14, dpi = 100, out.width="100%", out.height="100%", echo = FALSE}
  # Get the Behaviour duration plot and the behaviour names of the minimum
  printer <- plotBehaviourDuration(data = training_data, sample_rate = sample_rate, inc_outliers = inc_outlier_choice)
```
<!-- I've broken these two chunks up so I can better investigate what causes the report generation to be so slow. -->
<!-- See How long it takes to draw the behaviour plot -->
```{r Draw Behaviour Plot, fig.height=10, fig.width = 14, dpi = 100, out.width="100%", out.height="auto", fig.align='center', echo = FALSE}
  # Draw the plot on the report
  printer[[7]]
```
<br>
<p style = "text-align: center;">
`r paste0("<b>Figure 1:</b> Behaviour duration by activities in seconds. (N = ", printer[[9]], ")"  )`
</p>
<!-- Add a break between the plot and the data table -->
<br><br><br>
<!-- Plot the behaviour data table. -->
```{r draw data table, fig.height=8, fig.width = 14, dpi = 100, out.width="100%", out.height="100%", echo = FALSE}
  # Draw the dataframe of summary data
  kable(printer[[8]]) %>% 
    kable_styling(
      bootstrap_options = c("basic","hover"),
      position = "center",
      row_label_position = "center"
    )
```

<!-- Add a break in lines before header-->
<br><br>

<!-- Prints list of behaviours with the shortest duration followed by how long the shortest behaviour is   -->
### Summary
`r paste0("The <b>", dataset_name, " </b> dataset contains a total of: <br>")`
<ul>
`r paste0("<li> <b>", printer[[9]], "</b> identified individuals.</li>")`
`r paste0("<li> <b>", printer[[10]], " </b> identified behaviours.</li>")`
</ul>

#### Minimum Behaviour Duration:
`r paste0("Your behaviour(s) with the shortest minimum duration are: <br> ","<b>", paste(printer[[1]], collapse = ", "), "</b>")`
`r paste0("with a duration of: ", (printer[[2]]), " seconds", "<br><br>")`

<!-- Prints list of behaviours with the smallest median duration in seconds followed by how long the shortest behavior is -->
#### Median Behaviour Duration:
`r paste0("Your behaviour(s) with the shortest median duration are: <br> ","<b>", paste(printer[[3]], collapse = ", "), "</b>")`
`r paste0("with a duration of: ", (printer[[4]]), " seconds", "<br><br>")`

<!-- Prints list of behaviours with the smallest lower- duration in seconds followed by how long the shortest behavior is -->
#### Lower-Quantile Behaviour Duration:
`r paste0("Your behaviour(s) with the smallest lower quantiles are: <br> ","<b>", paste(printer[[5]], collapse = ", "), "</b>")`
`r paste0("with a duration of: ", (printer[[6]]), " seconds", "<br><br>")`

#### Recommendations:
`r paste0("Based on the <b>", dataset_name, "</b> dataset, it is recommended that you set your window length to be either:")`
<ul>
`r paste0("<li> <b>", printer[[6]], " seconds </b> based on your shortest lower quartile behaviour durations</li>")`
`r paste0("<li> <b>", printer[[4]], " seconds</b> based on your shortest median behaviour durations</li>")`
</ul>


