---
# Creating and assigning our global variables
title: "Visualisation Report"
# Output file type
output: html_document
# Set the date based on your computer
date: "`r Sys.Date()`"
# Set default parameters
params:
  base_path: "C:/Users/oaw001/Documents/SensitivityAnalyses"
  dataset_name: "Studd_Squirrel"
  sample_rate: "1"
---

```{r setup, include=FALSE}

# Set the variables of our other chunks
knitr::opts_chunk$set(
  # Set so that for all of our plots, it won't include the code.
  echo = FALSE,
  # Set the global figure width.
  fig.width = 5.625,
  # Set the global figure height.
  fig.height = 4.5)

  # We need to check if the user has all the right packages installed and if they don't install them.
# At this point we're just loading the packages but we need to change that.
library(data.table)
library(purrr)
library(tidyverse)
library(kableExtra)
```



```{r load data, include= FALSE}
# load in the raw data and cleaned feature data (e.g., remove redundant and NA features)
raw_data <- fread(file.path(base_path, "Data", "Other_data", paste0(dataset_name, "_other.csv")))
feature_data <- fread(file.path(base_path, "Data", "Feature_data", paste0(dataset_name, "_other_feature_data.csv")))
```

```{r Functions, include= FALSE}
# add in the functions for the various plots and analyses

# function for generating random colours
generate_random_colors <- function(n) {
  # Generate random red, green and yellow values.
  colors <- rgb(runif(n), runif(n), runif(n))
  return(colors)
}

```

# Commented out the function that plots the data.
{r plot data volume function, include=FALSE}
# function for plotting the volume (in minutes) of behaviour per individual
plotActivityByID <- function(data, frequency) {
  my_colours <- generate_random_colors(length(unique(data$ID)))
  # summarise into a table
  labelledDataSummary <- data %>%
    #filter(!Activity %in% ignore_behaviours) %>%
    count(ID, Activity)
  
  # account for the HZ, convert to minutes
  labelledDataSummaryplot <- labelledDataSummary %>%
    mutate(minutes = (n/frequency)/60)
  
  # Plot the stacked bar graph
  plot_activity_by_ID <- ggplot(labelledDataSummaryplot, aes(x = Activity, y = minutes, fill = as.factor(ID))) +
    geom_bar(stat = "identity") +
    labs(x = "Activity",
         y = "minutes") +
    theme_minimal() +
    scale_fill_manual(values = my_colours) +
    theme(axis.line = element_blank(),
          axis.text.x = element_text(angle = 45, hjust = 1),
          panel.border = element_rect(color = "black", fill = NA),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())
  
  return(plot_activity_by_ID)
}



## Title

text and descriptions

```{r plot data volume, echo = FALSE}
plotActivityByID(data = raw_data, frequency = sample_rate)
```