---
# Creating and assigning our global variables
title: "Behaviour Duration Report"
# Output file type
output: html_document
# Set the date based on your computer
date: "`r Sys.Date()`"
# Set default parameters
params:
  base_path: "C:/Users/user/Desktop/Oakleigh_Project/AccelerometerData/Accelerometer_Analysis"
  dataset_name: ""
  sample_rate: ""
---

```{r Setup, include=FALSE}

# Set the variables of our other chunks
knitr::opts_chunk$set(
  # Set so that for all of our plots, it won't include the code.
  echo = FALSE,
  # Set the global figure width.
  fig.width = 5.625,
  # Set the global figure height.
  fig.height = 4.5,
  # Stops messages from being produced in the output
  message = FALSE,
  # Stops warnings from appearing in the output
  warning = FALSE)

  # We need to check if the user has all the right packages installed and if they don't install them.
# At this point we're just loading the packages but we need to change that.
library(data.table)
library(purrr)
library(tidyverse)
library(kableExtra)

# Source all of our functions
source(file.path(params$base_path, "Scripts", "Functions.R"))
```

```{r Load in Data, include = TRUE}

# Source the Load Data script and attempt to load in the data
source(file.path(params$base_path, "Scripts", "LoadData.R"))

raw_data <- fread(file.path(base_path, "Data", "Other_Data", paste0(dataset_name, "_Training.csv")))

```

## Behaviour Classification of Individuals

### The data used for this split is: `r dataset_name`
<br>
Below is a graph of all individuals classed by behaviours in minutes.
The point of this plot is to use it to determine what your ideal window length is, which will be used to generate statistical and time series features.

### How to use:
Window lengths are used to condense multiple observations into a single row of data.

```{r plot data volume, fig.height=8, fig.width = 10, dpi = 600, out.width="100%", out.height="100%", echo = FALSE}
  # Get the Behaviour duration plot and the behaviour names of the minimum
  printer <- plotBehaviourDuration(data = raw_data, sample_rate = sample_rate, inc_outliers = inc_outlier_choice)
  # Draw the plot on the report
  printer[[7]]
  # Draw the dataframe of summary data
  #### Add a better formatted caption to the tabe.
  kable(printer[[8]], caption = "Summary of Activity Durations") %>% 
    kable_styling(
      bootstrap_options = c("basic","hover"),
      position = "center",
      row_label_position = "center"
      #fixed_thead = c(enabled = TRUE, background = "firebrick")
    )
```
<!-- Add a break in lines before header-->
<br><br>

<!-- Prints list of behaviours with the shortest durations followed by how long the shortest behaviour is   -->
#### Minimum Behaviour Duration:
`r paste0("Your behaviour(s) with the shortest minimum duration are: <br> ","<b>", paste(printer[[1]], collapse = ", "), "</b>")`
`r paste0("with a duration of: ", (printer[[2]]), " seconds", "<br><br>")`

<!-- Prints list of behaviours with the smallest median duration in seconds followed by how long the shortest behavior is -->
#### Median Behaviour Duration:
`r paste0("Your behaviour(s) with the shortest median duration are: <br> ","<b>", paste(printer[[3]], collapse = ", "), "</b>")`
`r paste0("with a duration of: ", (printer[[4]]), " seconds", "<br><br>")`

#### Lower-Quantile Behaviour Duration:
`r paste0("Your behaviour(s) with the smallest lower quantiles are: <br> ","<b>", paste(printer[[5]], collapse = ", "), "</b>")`
`r paste0("with a duration of: ", (printer[[6]]), " seconds")`


